---
title: "Hardware Survey Results"
author: "NTF"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)

hrdwr = as.data.frame(read.csv('C:\\Users\\ntfou\\OneDrive\\Documentos\\R_Code\\R_Code\\HardwareData.csv'))

```

## Hardware Survey Analysis   

General descriptive statistics from the Hardware Survey
Note: there are outliers and NAs that are filtered out of the data summarized below to improve the analysis

```{r hrdwr}
summary(hrdwr)
```

## Hardware Survey Across the Years


```{r Yrs, echo=FALSE}

hrdwr$Timestamp = as.POSIXct(hrdwr$Timestamp, format="%m/%d/%Y %H:%M", tz="UTC")

hrdwr$Year = as.integer(NA)

hrdwr = hrdwr %>%
  mutate(Year = year(Timestamp))

#removed 1970 outlier
tempYr = hrdwr %>%
  filter(Year > 2019)

ggplot(tempYr , aes(Year)) +
  geom_bar(alpha=.5, fill="black") +
  geom_text(aes(label = after_stat(count)), stat = "count", vjust = 2, colour = "white") 

```

## Hardware Survey - A look at the OS


```{r OpSys, echo=FALSE}

hrdwr$OpSys = str_wrap(hrdwr$OpSys, width = 10)

ggplot(hrdwr, aes(OpSys)) +
  geom_bar(alpha=.5, fill="black") +
  geom_text(aes(label = after_stat(count)), stat = "count", vjust = 0, colour = "black") 

```

## Hardware Survey - The CPU, a Distribution by GHz


```{r CPU, echo=FALSE}

hrdwr$OpSys = str_wrap(hrdwr$OpSys, width = 10)

ggplot(hrdwr, aes(x=CPU_ghz)) +
  geom_histogram(binwidth=.2, alpha=.5, fill="black") +
  coord_cartesian(xlim = c(1, 5)) 

```

## Hardware Survey - The CPU Cores


```{r CPU_Cores, echo=FALSE}

ggplot(hrdwr, aes(x=CPU_Cores)) +
  geom_bar(alpha=.5, fill="black") +
  geom_text(aes(label = after_stat(count)), stat = "count", vjust = 0, colour = "black") 

```

## Hardware Survey - RAM, a Distribution by Gbs


```{r RAM_gb, echo=FALSE}

ggplot(hrdwr, aes(x=RAM_gb)) +
  geom_bar(alpha=.5, fill="black") 

```

## Hardware Survey - Hard Drive, a Distribution by Gbs


```{r HrdDrv_gb, echo=FALSE}

ggplot(hrdwr, aes(x=HrdDrv_gb)) +
  geom_histogram(binwidth=1, alpha=.5, fill="black") +
  coord_cartesian(xlim = c(200, 600), ylim = c(0,60))

```

## Hardware Survey - Types of GPUs


```{r GPU_Desc, echo=FALSE}

hrdwr$GPUSumDesc = as.character(NA)

hrdwr$GPUSumDesc[grepl('nvidia|NVIDIA|Nvidia', hrdwr$GPU_Desc)] = 'NVIDIA'
hrdwr$GPUSumDesc[grepl('apple|Apple|APPLE', hrdwr$GPU_Desc)] = 'Apple'
hrdwr$GPUSumDesc[grepl('rtx|RTX', hrdwr$GPU_Desc)] = 'RTX'
hrdwr$GPUSumDesc[grepl('intel|Intel|INTEL', hrdwr$GPU_Desc)] = 'Intel'
hrdwr$GPUSumDesc[grepl('radeon|Radeon|RADEON', hrdwr$GPU_Desc)] = 'Radeon'

hrdwr = hrdwr %>%
  mutate(GPUSumDesc = ifelse(is.na(GPUSumDesc), 'Other', GPUSumDesc))

ggplot(hrdwr, aes(x=GPUSumDesc)) +
  geom_bar(alpha=.5, fill="black") +
  geom_text(aes(label = after_stat(count)), stat = "count", vjust = 0, colour = "black") 


```

## Hardware Survey - GPU Cuda Cores


```{r GPUCudaCores, echo=FALSE}

tempdf = hrdwr %>%
  filter(!is.na(GPUCudaCores))

ggplot(tempdf, aes(x=GPUCudaCores, rm.na = T)) +
  geom_histogram(binwidth=10, alpha=.5, fill = 'black') +
  coord_cartesian(xlim = c(0, 5000))


```